### 2015-03-19 evaluation.tex
update table
updated table

We conducted all experiments on ... We use the following software versions: Z3 4.1; SMACK 1.4; Clang/LLVM 3.5; \corral commit 3aa62d7425b5; Boogie commit d6a7f2bd79c9.

@@

In Table~\ref{tab:races}, we can notice that \whoop is much faster than \corral. For exampl, \whoop analyses the dtlk char driver in 6.51 seconds, whereas \corral requires 1287.05 seconds.

>>>>

We conducted all experiments on ... We use the following software versions: Clang/LLVM 3.5; SMACK 1.4; Z3 4.1; \corral commit 3aa62d7425b5; Boogie commit d6a7f2bd79c9.

@@

In Table~\ref{tab:races}, we can notice that \whoop is much faster than \corral. For example, \whoop analyses the dtlk char driver in 6.51 seconds, whereas \corral requires 1287.05 seconds.
